\documentclass[letterpaper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{helvet}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}
    \usepackage{hyperref}
    \usepackage{enumitem}
    \setlist{noitemsep}

    \renewcommand\familydefault{\sfdefault}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    % {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    {\hspace*{-18pt}\vspace*{6pt} #1}
    \vspace*{-6pt} \lineunder
}

\newcommand{\subheader} [1] {
    % {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
  \begin{center}
    {\hspace*{0pt}\vspace*{6pt} \large{\bf{#1}}}
    % \vspace*{-6pt} \lineunder
  \end{center}
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile =============================================================%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {James Puellmann}}\\
  james@puellmann.net $\cdot$ \href{http://resume.puellmann.net/resume.pdf}{resume.puellmann.net} \\
  268 E. Broadway, New York, NY 10002 $\cdot$ (314) 307-7435\\
\end{center}

%==== Summary =============================================================%
\header{Summary}
\vspace{1mm}

Senior infrastructure engineer, DevOps advocate, Agile veteran, Certified Scrum
    Master, and Linux enthusiast.
\vspace{1.5mm}

Extensive experience in tech leadership, system architecture, project and
    program management roles across diverse industries including Web Media,
    Publishing, E-Commerce, Finance, Energy, Government, IT Managed Services,
    IT consulting, healthcare, and software development.
\vspace{1.5mm}

Broad experience in DevOps Best Practices, Linux operating system build and
    deployment, container orchestration, infrastructure as code, configuration
    management and workflow automation for CI/CD pipelines.
\vspace{1.5mm}

Proven team leader, mentor, and teacher.

\vspace{3mm}

%==== Skills =============================================================%
\header{Skills \& Technical Proficiencies}
\begin{tabular}{ r l }
  \textbf{Computing Platforms:}      & Amazon AWS, Microsoft Azure, Kubernetes, Tanzu Kubernetes, VMware\\
  \textbf{Infrastructure as Code:}   & Terraform, Pulumi, CloudFormation, AzureRM, Bicep                \\
  \textbf{Configuration Management:} & Ansible, Chef, Puppet                                            \\
  \textbf{CI/CD:}                    & Azure DevOps, Gitlab CI, GitHub Actions, Jenkins                 \\
  \textbf{Operating Systems:}        & Ubuntu Linux, Fedora Linux, RHEL and CentOS Linux, Debian Linux  \\
  \textbf{Other:}                    & Docker, Git, Helm, Packer, Vagrant, Hashicorp Vault, Python      \\
\end{tabular}
\vspace{2mm}

%==== Experience =============================================================%
\header{Experience}
\vspace{1mm}
\textbf{World Wide Technology} \hfill New York, NY\\
\textit{Lead DevOps Engineer} \hfill Oct 2017 - Feb 2024\\
\vspace{-1mm}
\begin{itemize}
	\item DevOps Engineer
	\item Leader, Internal DevOps Practice
	\item Tech Mentor
	\item Tanzu Kubernetes Practice Lead
	\item DevOps Engineering Consultant
	\item Delivery Engineer
\end{itemize}

\textbf{The New York Times} \hfill New York, NY\\
\textit{Lead Engineer, Infrastructure} \hfill Jun 2013 - Oct 2017\\
\vspace{-1mm}
\begin{itemize}
	\item Infrastructure deployment and administration
	\item Software Repository and Patch Deployment Systems
	\item Standardized OS Image Provisioning
	\item Automation and Modernization of Legacy Software Systems
	\item Configuration Management and Continuous Software Integration
\end{itemize}

\textbf{CenturyLink (as Savvis)} \hfill New York, NY and St. Louis, MO\\
\textit{Program Manager} \hfill Oct 2006 - Jun 2013\\
\vspace{-1mm}
\begin{itemize}
	\item Program Manager, AMC Networks
	\item Systems Architect, PR Newswire
	\item Technical Operations Manager, Hallmark Cards
	\item Technical Operations Manager, American Stock Exchange
	\item Sr. Systems Engineer, American Stock Exchange
\end{itemize}

\textbf{Unisys} \hfill St. Louis, MO\\
\textit{Sr. Linux Administrator, USDA Web Farm} \hfill Nov 2002 - Oct 2006\\
\vspace{-1mm}
\begin{itemize}
	\item Sr. Linux Engineer and Linux Subject Matter Expert for USDA Web Farm
	\item System Administration: Linux, Apache, Tomcat, HP-UX
\end{itemize}

\textbf{Amdocs} \hfill St. Louis, MO\\
\textit{Configuration Control Administrator} \hfill Jun 2000 - Oct 2002\\
\vspace{-1mm}
\begin{itemize}
	\item Team Lead, Amdocs Infrastructure Configuration and Control Group
\end{itemize}

\pagebreak

%==== Projects =============================================================%
\header{Projects, Roles, and Responsibilities}

{\textbf{Lead DevOps Engineer}, WWT Loyalty Program for Global Retail Chain} \\
\hspace{5mm}{\sl (Terraform, Microsoft Azure, Azure DevOps, Amazon AWS)} \\
Led Infrastructure and DevOps efforts for a team of 30+ developers to rebuild
  a customer loyalty platform for a global retail chain. \\
Strengthened internal DevOps organization in fundamentals of software delivery and
  site reliability engineering (SRE) by mentoring, interviewing, and leading
  technical demos and proof-of-concept labs.\\
Designed and implemented IaC and full CI/CD pipeline for ten software
  repositories to deploy new architecture into Azure and integrate with legacy
  AWS deployments.\\
\vspace*{2mm}

{\textbf{DevOps Engineer}, WWT Website Deployment for Medical Device Manufacturer} \\
\hspace{5mm}{\sl (Terraform, Ansible, Microsoft Azure, Azure DevOps)} \\
Architected and deployed IaC and CI/CD Pipeline for new Azure cloud
  architecture to host website and CMS application for medical device
  manufacturer.\\
\vspace*{2mm}

{\textbf{Consulting DevOps Engineer}, WWT Azure Migration for Regional Bank } \\
\hspace{5mm}{\sl (Microsoft Azure, Azure DevOps, Terraform, Ansible)} \\
Consulted as Subject Matter Expert on DevOps, IaC, and CI/CD for a large regional
  bank\textquotesingle{}s migration to the Azure cloud.\\
\vspace*{2mm}

{\textbf{Practice Lead}, WWT Tanzu Kubernetes Platform Services Offering} \\
\hspace{5mm}{\sl (VMware Tanzu Kubernetes Grid (TKG), Kubernetes, Terraform, Ansible, Helm,
  VMware ESX, Amazon AWS)} \\
Led technical execution for Tanzu Kubernetes Product offering as partnership
  between WWT and VMware. \\
Architected, installed and configured Kubernetes clusters and consulted with
  client technical and executive roles on ongoing cluster administration.\\
\vspace*{2mm}

{\textbf{DevOps Engineering Consultant}, Multiple WWT Clients} \\
\hspace{5mm}{\sl (The Three Ways, Theory of Constraints, The Five Pillars, SRE, Kaizen, Lean, Kanban, Scrum)} \\
Assessed client engineering teams to identify and evaluate DevOps practices
  strengths and weaknesses.\\
Developed executive strategies for enhancing DevOps excellence within IT
  organizations through mentoring and collaboration with executive leadership.
Embedded within client infrastructure and software engineering teams to improve
  DevOps workflow by teaching, mentoring, and leading by example.\\
\vspace*{2mm}

{\textbf{Delivery Engineer}, WWT Microservices Replatform for National Retail Chain} \\
\hspace{5mm}{\sl (Kubernetes, KOPS, Helm, Amazon AWS, Ansible, Terraform, GitLab CI, Packer, Docker, Jenkins, PostgreSQL)} \\
Designed and built vanilla Kubernetes environment in AWS for retail chain
  restaurant online ordering system to leverage reliability and scalability of
  a cloud-based microservices platform.\\
Implemented all IaC and end-to-end CI/CD pipelines for Kubernetes
  infrastructure and AWS cloud environments.\\
\vspace*{2mm}

{\textbf{Lead Engineer: Infrastructure}, The New York Times} \\
\hspace{5mm}{\sl (Terraform, Puppet, Packer, Vault, Git, Python, Travis,
  Jenkins, Postgres)} \\
Designed and built single, standardized OS image for deployment across three
  infrastructure platforms. \\
Designed and built CI/CD pipelines and automated testing platform for same. \\
Built initial POC infrastructure for service migration to GCP cloud. \\
\vspace*{2mm}

%==== Awards =============================================================%
\header{Awards \& Recognition}

% \textbf{High Performing Employee} \hfill Mar, 2022\\
% \hspace*{5mm} Practice Lead for Tanzu Kubernetes product offering.\\
% \vspace*{2mm}
%
% \textbf{High Performing Team Award} \hfill Feb, 2021\\
% \hspace*{5mm} DevOps Consultant for high profile credit union consulting project.\\
% \vspace*{2mm}
%
% \textbf{High Performing Team Award} \hfill Nov, 2020\\
% \hspace*{5mm} DevOps Consultant for Agile \& DevOps adoption program at a credit union.\\
% \vspace*{2mm}
%
% \textbf{High Performing Team Award} \hfill Jan, 2019\\
% \hspace*{5mm} Delivery Engineer for large retail chain website redesign.\\
% \vspace*{2mm}
%

\textbf{High Performing Employee}, Practice Lead for Tanzu Kubernetes product
offering. \hfill Mar, 2022\\
% \vspace*{2mm}

\textbf{High Performing Team Award}, DevOps Consultant for high profile credit
union consulting project. \hfill Feb, 2021\\
% \vspace*{2mm}

\textbf{High Performing Team Award}, DevOps Consultant for Agile adoption
program at a credit union. \hfill Nov, 2020\\
% \vspace*{2mm}

\textbf{High Performing Team Award}, Delivery Engineer for large retail chain
website redesign. \hfill Jan, 2019\\
\vspace*{2mm}

%==== Education =============================================================%
\header{Education and Certifications}
\textbf{Bachelor of Science, Mathematics} \hfill University of Missouri -
Columbia \hfill  May, 2000\\
\vspace{2mm}

%==== Education =============================================================%
\header{Education and Certifications}
\begin{tabular}{ l l }
  \textbf{RHCE 804005037814534}: Jun, 2008       & \textbf{Certified Scrum Master, Scrum Alliance}: Sep, 2017 \\
  \textbf{GitLab Solutions Architect}: Dec, 2020 & \textbf{HashiCorp Certified Terraform Associate}: Jul, 2021 \\
\end{tabular}
\vspace{2mm}

\end{document}

